Do return series have power-law tails with the same index?

### 2017-04-13 papers/FX/draft.tex
Revised the FX paper as well as the R scripts.

\subsection{A test of equal tail indices based on Hill estimator}
From \eqref{eq:2} one can deduce
\begin{equation}
  \label{eq:x1}
  \sqrt k (\hat \alpha_A - \hat \alpha_B) \overset{d}{\to} N(0, \alpha_A^2 - \alpha_B^2)  
\end{equation}
where $\hat \alpha_A$ and $\hat \alpha_B$ are Hill estimates of
$\alpha_A$ and $\alpha_B$, the tail indices of two series $A$ and
$B$. The weak convergence of \eqref{eq:x1} allows one to construct a
test of the equality of $\alpha_A$ and $\alpha_B$.

>>>>

\subsection{A test of equal tail indices based on Hill estimator}
Suppose we have two iid series $X_1, \dots, X_n \sim F_X$ and
$Y_1, \dots, Y_n \sim F_Y$. Both $F_X$ and $F_Y$ have power-law tails
with indices $\alpha_X$ and $\alpha_Y$, respectively.
From \eqref{eq:2} one can deduce
\[
\sqrt k
\begin{pmatrix}
  {\hat \alpha_X - \alpha_X} \\
  {\hat \alpha_X - \alpha_X} \\
\end{pmatrix} \overset{d}{\to}
\begin{pmatrix}
  Z_X \\
  Z_Y
\end{pmatrix}
\sim
N\left(
0, \text{diag}(\alpha_X^2, \alpha_Y^2)
\right)
\]
where $\hat \alpha_X$ and $\hat \alpha_Y$ are Hill estimates of
$\alpha_X$ and $\alpha_Y$. Then it follows from continuous mapping
theorem
\begin{equation}
  \label{eq:x1}
  \sqrt k [(\hat \alpha_X -\alpha_X) - (\hat \alpha_Y - \alpha_Y)]
  \overset{d}{\to}
  Z_X - Z_Y \sim N(0, \alpha_X^2 + \alpha_Y^2)
\end{equation}
The weak convergence of \eqref{eq:x1} allows one to construct a test
of the equality $\alpha_X = \alpha_Y$. As the null hypothesis, assume
$\alpha_X = \alpha_Y$. Under this hypothesis \eqref{eq:x1} means the
test statistic
$\hat \alpha_X - \hat \alpha_Y \overset{d}{\to} N(0, \alpha_X^2 +
\alpha_Y^2)$
We apply this test to the equities in the ``Energy'',
``Consumder Staples'' and ``Information Technology''
sectors of the S\&P 500 index. The results are shown in
\ref{fig:PairTest}.
\begin{figure}[htb!]
  \begin{minipage}{0.5\linewidth}
    \includegraphics[
      width=\textwidth,
    ]{HillTest_Energy.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.5\linewidth}
    \includegraphics[
      width=\textwidth,
      trim={0.3cm, 1cm, 1cm, 1cm}, clip
    ]{Hoga_Energy_pair.pdf}
  \end{minipage}
  \caption{Test of equal tail indices}
  \label{fig:PairTest} 
\end{figure}
